---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dossier

<!-- badges: start -->
[![R-CMD-check](https://github.com/huizezhang-sherry/dossier/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/huizezhang-sherry/dossier/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/huizezhang-sherry/dossier/graph/badge.svg)](https://app.codecov.io/gh/huizezhang-sherry/dossier)
<!-- badges: end -->

The `dossier` package provides tools to analyze and compare decisions made in the data analysis across multiple applied studies on the same topic. It helps explore the "garden of forking paths" by highlighting patterns, similarities, and differences in how analyses are conducted.

## Installation

<!-- You can install the released version of dossier from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("dossier") -->
<!-- ``` -->

<!-- And  -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("huizezhang-sherry/dossier")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE}
library(dossier)
library(dplyr)
library(text)
raw_df <- readr::read_csv(system.file("papers.csv", package = "dossier"))
(tbl_df <- as_decision_tbl(raw_df))
```
 
```{r}
# select the variable-type pair to compare papers
count_variable_type(tbl_df) 
(df <- tbl_df |> filter_var_type(n = 6)) # first 6 variable-type pairs

# subset to papers with at least 3 decisions (include all)
count_paper_decisions(df)
(paper_df <- df |> filter_papers(n_value = 3))

count_paper_pair_decisions(paper_df)
```


```{r}
# calculate the text embed
embed_df <- paper_df |> compute_text_embed()
# calculate decision similarity
(distance_decision_df <- calc_decision_similarity(paper_df, embed = embed_df))
# aggregate from decision similarity to paper similarity
(distance_df <- distance_decision_df |> calc_paper_similarity())
```

## Diagnostics and visualization

```{r}
diag_decision_ppp(distance_decision_df, distance_df)
view_pairs(paper_df, distance_decision_df, "braga", "zanobetti")
```

```{r echo = FALSE, fig.height=4}
library(ggplot2)
library(patchwork)
library(ggdendro)
# cluster the paper by hierarchical clustering and multi-dimensional scaling
hclust_res <- run_hclust(distance_df, "ave")
mds_res <- run_mds(distance_df)

get_most_common_method <- function(df, cols = c("time_parameter_method",
                                                "humidity_parameter_method",
                                                "temperature_parameter_method")) {
  df %>%
    pivot_decision_tbl_wider() |>
    rowwise() %>%
    mutate(method = {
      vals <- c_across(all_of(cols))
      vals <- vals[!is.na(vals)]
      if (length(vals) == 0) NA_character_
      else names(sort(table(vals), decreasing = TRUE))[1]
    }) %>%
    ungroup() |>
    select(paper, method)
}


# find the most common method for each paper for plotting
method_df <- paper_df |> get_most_common_method() # from `helper.R`
hclust_res$labels <- hclust_res$labels |> left_join(method_df, by = c("label" = "paper"))
mds_df <- mds_res |> left_join(method_df, by = "paper")

# plot the dendrogram and multi-dimensional scaling
p2 <- ggplot() +
  geom_segment(data = segment(hclust_res), aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_text(data = hclust_res$labels,
            aes(x = x, y = y, label = label, color = method, hjust = 0),
            size = 3) +
  coord_flip() +
  theme_void() +
  scale_color_brewer(palette = "Dark2") +
  scale_y_reverse(expand = c(0.2, 0))

p3 <- mds_df |> ggplot(aes(x = V1, y = V2)) +
  ggrepel::geom_text_repel(aes(label = paper, color = method)) +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_brewer(palette = "Dark2") +
  ggtitle("Multi-dimensional scaling")

(p2 | p3) & theme(legend.position = "bottfom")

```

